---
title: "MLproject"
output: html_document
---

Background:

Data: Six young health participants were asked to perform one set of 10 repetitions of the Unilateral Dumbbell Biceps Curl in five different fashions (variable “classe”). Class A corresponds to the specified execution of the exercise, while the other 4 classes correspond to common mistakes.

Task: This program uses the “Random Forest” with n-fold cross validation in the R caret package to the “classe” variable given a list of input features. Below is a step by step process:

1. Load the data:

```{r, hide=TRUE}
library(caret)
trainData_URL<-"http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
testData_URL<-"http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
trainData<-read.csv(trainData_URL,na.strings=c("NA",""))
testData<-read.csv(testData_URL,na.strings=c("NA",""))
```

2. Data clean-up (get rid of trivial or mostly “NA” columns)

```{r, hide = TRUE}
trainData<-trainData[,7:160]
nonNA_data<-apply(!is.na(trainData),2,sum)>19621
trainData<-trainData[,nonNA_data]
```

3. Data partition

```{r, hide = TRUE}
InTrain<-createDataPartition(y=trainData$classe,p=0.5,list=FALSE)
training1<-trainData[InTrain,]
```


5. Train the model

```{r, hide = TRUE}
fit_rf<-train(classe~.,data=training1,method="rf",
                trControl=trainControl(method="cv",number=5),
                prox=TRUE,allowParallel=TRUE)
```

Result (accuracy is satisfactory):
```{r, hide = TRUE}
print(fit_rf)
```
